Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-22 WRITEUP/ms.tex
proof-read

The \ncode{GILDAS} package was used to reduce and analyze the visibility data
which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$ = 1.451 mJy \kms
beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is created by averaging over all the line-free channels. This
yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

@@

The \ncode{MIRIAD} package was used to calibrate the visibility data which are
then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA = 8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
over a channel width of 25 MHz. An rms noise of
$\sigma$ = 0.831 mJy beam\pmOne is reached by averaging over the
line-free channels.

@@

Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We use \ncode{AIPS} to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

@@

The emission in the IRAC images is slightly extended. We thus use the
{\it HST} image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the IRAC imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

Extraction of the {\it Herschel}/SPIRE photometry was
carried out using SUSSEXTractor within Herschel Interactive
Processing Environment (HIPE; \citealt{Ott10a})
over the Level 2 maps obtained from the Herschel Science Archive.
These maps were processed by the SPIRE pipeline
version 13.0 within HIPE. The SUSSEXtractor task estimates
the flux density from an image convolved with a kernel
derived from the SPIRE beam. The flux density
measured by SUSSEXtractor is additionally confirmed
using the Timeline Fitter, which performs photometry
by fitting a 2D elliptical Gaussian to the Level 1 data at the
source position given by the output of SUSSEXtractor.

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{sec:lensmodel} %DONE
At the angular resolution of the \bco data, the images are resolved
but not within the multiply lensed emission (i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Model of each slice in \Fig{model} thus provides
properties on the intrinsic kinematics. The slices
are obtained by binning the data (over the full linewidth
$\sim$700\kms; see \Sec{CO21}) by five channels (i.e., into seven slices)
 to increase the SNR.

The lens mass distribution is modeled using a singular isothermal
ellipsoid (SIE) profile, which is described by five free parameters: the
positional offset in R.A. and Dec. relative to an arbitrary chosen
fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
position angle. We use the VLA radio continuum emission toward
the foreground galaxy to initialize the positional offset. We impose a
uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec.,
motivated by the astrometry uncertainties in the VLA image as well as
the uncertainties provided by previous SIE lens model (C06).
We initialize the Einstein Radius based on the model parameters reported by C06
and impose a uniform prior using $\pm$3$\sigma$ of their uncertainties.
The sources are modeled using elliptical Gaussian profiles, which are
parameterized by six free parameters: the positional offset in R.A.
and Dec. relative to the lens, the intrinsic flux density, the effective
radius, the axial ratio, and the position angle. The position of each source
is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
and the effective radius is allowed to vary from 0\farcs01$-$2".

@@

\subsubsection{Interpretation and Caveats} \label{sec:caveat} %DONE
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient across the source plane, which is
indicative of a disk geometry. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
and C06, who find evidence for an interacting dusty galaxy.
Spatially, the red velocity component of the CO also coincides with this
component F. While we cannot quantify the type of
merger (major v.s. minor) with a mass ratio given the
spatial resolution, the symmetric velocity gradient may lean support
towards a minor merger.

We emphasize that the spatial resolution of the data at hand
is a few arcsec, which implies that despite the high SNR and spectral
resolution, this data is insufficient to constrain the
intrinsic sizes of the lensed galaxies, and thus the magnification
factors ares likely under-predicted.
We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15

@@

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
\input{table_magFactor}
Previous lens models of RXJ1131 find conspicuous
differential lensing effect across {\it HST}
$H$-, $V$-, and $I$-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission, arising from \SF.
The highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO, where the redshifted
emission is apparently much brighter than that in the
blueshifted emission, consistent
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).

@@

We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is inequivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the C06 lens model (converted to
our cosmology) over the {\it HST} $I$-band image.
We note that the source plane half-light radius varies substantially with
wavelength: $R_e$ $\sim$\,4kpc and $\sim$7\,kpc based on models over
$V$-band \citep{Brewer08a} and $H$-band (C06), respectively.
This discrepancy arises owing to the exclusion of the more
diffused emission in $V$-band (rest-frame UV),
which traces recent massive \SF.
% On the other hand, $I$-band traces the more evolved stellar population.
This indicates that the molecular gas may be ....
DR: ok, let's discuss this.

Using this $V_{\rm rot}$, we find a dynamical mass of
$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
within the CO-emitting region. If we instead consider the
line peak separation from the
\bco line profile $\Delta v_{\rm sep}/2 \sim$110\,\kms, we find
$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 1.8\E{10}\,\Msun.
DR: here, I list the extrema for possible Mdyn given our data,
should I say anything more?
We correct for the inclination effect using the
morphological axial ratio from the reconstructed image (Figure 3 in C06), where
the minor axis is 1\farcs8 and the major axis is 3\farcs25.
We thus find an inclination angle of 56.4\degr, which is consistent with the
observed unobscured AGN and an observable double peak line profile.
The dynamical mass is then
2.5\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
Since this quantity is derived under the assumption that the gas is
virialized, which is highly unlikely given the velocity dispersion and the
presence of a close companion, our estimate is
at most a lower limit. We caution that this analysis is
based on limited spatial
resolution data and will be verified by future higher-resolution
observations.

\subsection{SED modeling} \label{sec:SED}
By fitting a power-law spectrum $S_\nu \propto \nu^\alpha$ to the decomposed
IRAC photometry. We find a spectral index of $\alpha\sim-$1.9 and
$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
This is consistent with the mean spectral slope of optical quasars
(optically-selected) ($\alpha\sim-$1, Elvis et al. 1994;
Neugebauer et al. 1979).
For comparison, broad-line AGN from the AGN and Galaxy
Evolution Survey (AGES, C. S. Kochanek et al., in prep) have 3.6$-$8 \micron slopes of $\alpha$ = $-$1.07$\pm$0.53 (Stern et al. 2005).

@@

We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side.
We include the IRAS 60\micron and 100\micron upper limits to constrain the dust peak.
We also fit SED models including the decomposed 24.0\micron data (see \Sec{photometry})

Spitzer mid-IR spectroscopy of local ULIRGs will indicate the appropriate luminosity fraction that needs to be assigned to the AGN for ULIRGs before and after nuclear coalescence.
ULIRG Lir
Our SED model find a rest-frame characteristic dust temperature of BLAH (cf. 60-70K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10)

@@

We fit modified blackbody functions to
to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt
BLAH (rest frame; Dunne et al. 2003).)
We added blah\% calibration uncertainties on the PdBI data.

We check convergence of our chains by requiring that the autocorrelation length for each model parameter is
several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
The code treats the instrument response.
flux using the set of photometric filters used to obtain the observations.

identical to the modified blackbody fit,
where the Wien side is removed and replaced by MIR power-law consistent with any mid-IR data available.
We find a power-law slope of BLAH,
Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).

% upper limit using decomposed 24 um
% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
% parameter estimation problem
For these parameter estimation problems using MCMC to sample,
the full answer is the full joint posterior PDF.
We here report the summary statistics (global mode (where min. chi),
marginal mode (in log file),
posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.

\subsection{Physical properties}
In this section, we derive the gas properties of RXJ1131 based on \bco,
and compare the derived quantities against those reported by
\citet[; hereafter C13]{Combes13a}, which is the largest sample of
ULIRGs at intermediate redshift (0.6\,$<$\,$z$\,1.0) with CO measurements,
to place RXJ1131 in context of existing studies. Their results are
based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.

%line width & extent
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the \bco line profile are
consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
than in local ULIRGs (240\,\kms; \citet[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution (size) with local ULIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the
sample of disk-like ULIRGs studied by \citet{Ueda14a},
who find an average radius of 3.5\,$\pm$\,2.3\,kpc,
(with a range from 1.1 kpc to 9.3 kpc).
This indicates that the positive correlation in the linewidth-size relation
holds in ULIRGs at intermediate redshifts. Yet we cannot quantify this further
with the data represented in this paper.
{\bf implication on this in discussion}
% gas mass
To derive the molecular gas mass, we first correct for lensing magnification
using the respective magnification factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing. This yields
$I$\,=\,5.9$\pm$2.7 Jy\,\kms, where the uncertainty includes those on
the magnification factors. This includes the CO emission from the companion
as the resolution of our data do not allow us decompose its contribution
to the total line flux. Without direct \rot{1}{0} measurements,
we derive \rot{1}{0} intensity
using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
solely to facilitate a comparison with the C13 sample. For the same reason, we
adopt a luminosity-to-mass conversion factor of
\alphaco\,=0.8 (K \kms pc$^2$)\pmOne. This yields
\Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\Lsun and a gas mass
of (2.8$\pm$1.3)\,\E{10} \Msun in RXJ1131. This is likely
an overestimation due to a contribution from the companion, but is
nevertheless consistent with C13 ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
uncertainties. Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
$f_{\rm gas-dust}$\,=\,BLAH, consistent with Combes+13: 206 ?
 Typical local (U)LIRGs are found to have a
gas-to-dust mass ratio of 200–350 (Sanders et al. 1991; Contini
& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).

% SFE and depletion time

@@

\subsubsection{Gas properties}
% Gas, dynamical, etc
Since RXJ1131 has a companion, i.e. not dynamically relaxed, the dynamical mass estimate using a virial estimator is likely underestimated.

\subsubsection{SF and Molecular Gas}
C06: 814

>>>>

The \ncode{gildas} package was used to reduce and analyze the visibility data
which are then imaged and deconvolved using the CLEAN algorithm with ``natural"
weighting. This yields a synthesized clean beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA = 13\degr).
The final rms noise is $\sigma$ = 1.451 mJy \kms
beam\pmOne over 10 MHz (21.5 \kms). The continuum image at $\nu_{\rm cont}\sim$139\,GHz
is created by averaging over all the line-free channels. This
yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

@@

The \ncode{miriad} package was used to calibrate the visibility data which are
then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA = 8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
over a channel width of 25 MHz. An rms noise of
$\sigma$ = 0.831 mJy beam\pmOne is reached by averaging over the
line-free channels.

@@

Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We use \ncode{aips} to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

@@

The emission in the IRAC images is slightly extended. We thus use the
{\it HST} image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

Extraction of the {\it Herschel}/SPIRE photometry was
carried out using \ncode{sussextractor} within Herschel Interactive
Processing Environment (HIPE; \citealt{Ott10a})
over the Level 2 maps obtained from the Herschel Science Archive.
These maps were processed by the SPIRE pipeline
version 13.0 within HIPE. The \ncode{sussextractor} task estimates
the flux density from an image convolved with a kernel
derived from the SPIRE beam. The flux density
measured by \ncode{sussextractor} is additionally confirmed
using the Timeline Fitter, which performs photometry
by fitting a 2D elliptical Gaussian to the Level 1 data at the
source position given by the output of \ncode{sussextractor}.

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{sec:lensmodel} %DONE
At the angular resolution of the \bco data, the images are resolved
but not within the multiply lensed emission (i.e., sub-optimal for
performing lens modeling). Nevertheless, the high spectral
resolution of this data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21highO}).
Hence, with the high SNR, we reconstruct the intrinsic gas
dynamics by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit (\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of
the code). Model of each slice in \Fig{model} thus provides
properties on the intrinsic kinematics. The slices
are obtained by binning the data over the full linewidth
$\sim$700\,\kms by five channels,
that is, into seven slices, to increase the SNR.

The lens mass distribution is modeled using a singular isothermal
ellipsoid (SIE) profile, which is described by five free parameters: the
positional offset in R.A. and Dec. relative to an arbitrary chosen
fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
position angle. We use the VLA radio continuum emission toward
the foreground galaxy to initialize the positional offset. We impose a
uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec.,
motivated by the astrometry uncertainties in the VLA image as well as
the uncertainties provided by previous SIE lens model (C06).
We initialize the Einstein Radius based on the model parameters reported by C06
and impose a uniform prior using $\pm$3$\sigma$ of their uncertainties.
The sources are modeled using elliptical Gaussian profiles, which are
parameterized by six free parameters: the positional offset in R.A.
and Dec. relative to the lens, the intrinsic flux density, the effective
radius, the axial ratio, and the position angle. The position of each source
is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
and the effective radius is allowed to vary from 0\farcs01$-$2$^{\prime\prime}$.

@@

\subsubsection{Interpretation and Caveats} \label{sec:caveat} %DONE
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient across the source plane, which is
indicative of a disk-like galaxy. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
and C06, who find evidence for an interacting dusty galaxy.
Spatially, the red velocity component of the CO also coincides with this
component F. While we cannot quantify the type of
merger (major v.s. minor) with a mass ratio given the
spatial resolution, the symmetric velocity gradient lean support
to the case of a minor merger.

We emphasize that the spatial resolution of the data at hand
is a few arcsec, which implies that despite the high SNR and spectral
resolution, this data is insufficient to constrain the
intrinsic sizes of the lensed galaxies, and thus the magnification
factors are likely under-predicted.
We will discuss this further in the following section. % magnification factor is underpredicted, see Bussmann15

@@

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
\input{table_magFactor}
Previous lens models of RXJ1131 find evidence for
differential lensing across {\it HST}
$H$-, $V$-, and $I$-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission. The highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO, where the redshifted
emission is apparently much brighter than that in the
blueshifted part, consistent
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).

@@

We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is inequivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (C06; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4kpc and $\sim$7\,kpc in $V$-band
\citep{Brewer08a} and $H$-band (C06), respectively.
This discrepancy arises owing to the exclusion of the more
diffused emission in $V$-band (rest-frame UV),
which traces young massive stars. 
The $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than other bands.
On the other hand, the molecular gas (fuel for \SF) is more compact
than the more evolved stellar population, as traced by $I$ and $H$-bands.
This is consistent with the picture that stars diffuse outward
after their formation \citep{Calzetti01a}.

Using the $V_{\rm rot}$ from last paragraph, we find a dynamical mass of
$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$\,=\,17\E{10}\,\Msun enclosed
within the CO-emitting region. If we instead consider the
line peak separation from the
\bco line profile $\Delta v_{\rm sep}/2 \sim$110\,\kms, we find
$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$ = 1.8\E{10}\,\Msun.
{\bf DR: here, I list the extrema for possible Mdyn given our data,
should I say anything more?}
We correct for the inclination effect using the
morphological axial ratio from the reconstructed image (Figure 3 in C06), where
the minor axis is 1\farcs8 and the major axis is 3\farcs25.
We thus find an inclination angle of 56.4\degr, which is consistent with the
observed unobscured AGN and an observable double peak line profile.
The dynamical mass is then
2.5\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
Since this quantity is derived under the assumption that the gas is
virialized, which is highly unlikely given the velocity dispersion and the
presence of a close companion, our estimate is
at most a lower limit. We caution that this analysis is
based on limited spatial
resolution data and will be verified with future higher-resolution
observations.

\subsection{SED modeling} \label{sec:SED}
By fitting a power-law spectrum $S_\nu \propto \nu^\alpha$ to the decomposed
IRAC photometry. We find a spectral index of $\alpha\sim-$1.9 and
$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
This is consistent with the mean spectral slope of optical quasars
($\alpha\sim-$1, Elvis et al. 1994; Neugebauer et al. 1979).
For comparison, broad-line AGN from the AGN and Galaxy
Evolution Survey (AGES, C. S. Kochanek et al., in prep) have 3.6$-$8
\micron slopes of $\alpha$ = $-$1.07$\pm$0.53 (Stern et al. 2005).

@@

% describe the SED model
We fit SED models to the photometry from BLAH$-$BLAH \micron
using a modified-blackbody function
with a power-law attached to the blue side.
% We added blah\% calibration uncertainties on the PdBI data.
We include
the IRAS 60\micron and 100\micron upper limits
to constrain the dust peak. We also fit SED models
including the decomposed 24.0\micron data.
identical to the modified blackbody fit,
where the Wien side is removed and replaced by MIR power-law consistent with any mid-IR data available.
We find a power-law slope of BLAH,
Previous studies find that in the absence of mid-IR data, a powerlaw slope of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).

% describe mbb_emcee
We check convergence of our chains by requiring that the autocorrelation length for each model parameter is
several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
The code treats the instrument response.
flux using the set of photometric filters used to obtain the observations.
% parameter estimation problem
For these parameter estimation problems using MCMC to sample,
the full answer is the full joint posterior PDF.
We here report the summary statistics (global mode (where min. chi),
marginal mode (in log file),
posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.

% upper limit using decomposed 24 um
% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
Our SED model find a rest-frame characteristic dust temperature of BLAH
(cf. 60$-$70\,K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10),
\fir (rest-frame 42.5-122.5 \micron) of blah, and a dust mass of blah.
For the mass absorption coefficient, we adopt BLAH (rest frame; Dunne et al. 2003).

@@

@@

\subsection{Gas properties}
In this section, we derive the gas properties of RXJ1131 based on \bco,
and compare the derived quantities against those reported by
\citet[hereafter C13]{Combes13a}, which is the largest sample of
ULIRGs at intermediate redshift (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements,
to place RXJ1131 in context of existing studies. Their results are
based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.

\subsubsection{Linewidth \& Sizes}
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
than in local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution (size) with local ULIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the average in the
sample of disk-like ULIRGs studied by \citet{Ueda14a},
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
(with a range from 1.1 kpc to 9.3 kpc).
This indicates that the positive correlation in the linewidth-size relation
holds at intermediate redshifts. Yet we cannot quantify this further
with the data represented in this paper.

\subsubsection{Gas Mass}
To derive the molecular gas mass, we first correct for lensing magnification
using the respective magnification factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing. This yields
$I$\,=\,5.9$\pm$2.7 Jy\,\kms, where the uncertainty includes those on
the magnification factors. 
We note that the derived intensity includes emission from the companion
as the spatial resolution of our data do not allow us decompose its contribution
to the total line flux.

Without direct \rot{1}{0} measurements,
we derive \rot{1}{0} intensity
using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
solely to facilitate a comparison with the C13 sample. For the same reason, we
adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields
\Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\Lsun and a gas mass
of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
an overestimation due to a contribution from the companion, but is
nevertheless consistent with the C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
uncertainties.

% gas-to-dyn ratio
Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
$f_{\rm gas-dust}$\,=\,BLAH, consistent with Combes+13: 206 ?
 Typical local (U)LIRGs are found to have a
gas-to-dust mass ratio of 200$-$350 (Sanders et al. 1991; Contini
\& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).

\subsubsection{SFE and Depletion Time}
dot dot dot
